Automated Topic Naming

### 2012-01-15 ese/ese.tex
- [X] Most commits we observed had commit comments. Can you be more precise      here and quantify?          - MaxDB 7.500          -    Min. 1st Qu.  Median    Mean 3rd Qu.    Max.               5.0    83.0    94.0   111.5   138.0  1149.0          - summary(v$V1)            Min. 1st Qu.  Median    Mean 3rd Qu.    Max.            5.0    83.0    94.0   111.5   138.0  1149.0          - summary(v$V2)            Min. 1st Qu.  Median    Mean 3rd Qu.    Max.            1.000   6.000   8.000   7.872   8.000 110.000          - summary(mysql$V1)            Min. 1st Qu.  Median    Mean 3rd Qu.    Max.

For each project, we used source control commit comments, the messages
that programmers write when they commit revisions to a source control
repository. 
Most commits we observed had commit comments.
Commit comments are often studied by researchers, as they are the most readily accessible source of project interactions, and developers are often
required to create them by the repository mechanism (e.g., Git).  Additionally, relying only on commit comments makes our approach more generalizable,
as we do not assume the presence of other artifact corpora.
%This is the most readily accessible source of project interactions for outside researchers, since developers often or always (e.g., Git) write such
%message. Our approach is more generalizable if it does not assume the presence of other corpora. 
%bug trackers and email-list archives were not available for both projects. 
An example of a typical commit message, from MySQL, is: \textit{``history annotate diffs bug fixed (if mysql\-\_real\-\_connect() failed there were
two pointers to malloc'ed strings, with memory corruption on free(), of course)''}. 
We extracted these messages and indexed them by creation time. 
We summarized each message as a word distribution minus stop-words such as ``\emph{the}'' and ``\emph{at}''. 
%Stemming was performed in the later stages of our analysis. % WAS IT?

@@

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input messages. 
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. 
These $N$ word distributions effectively form \emph{topics}: cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.

>>>>

For each project, we used source control commit comments, the messages
that programmers write when they commit revisions to a source control
repository. 
Most commits we observed had commit comments (90\% in MySQL 3.23,
98.5\% in PostgreSQL and 99.99\% in MaxDB 7.500).
Commit comments are often studied by researchers, as they are the most readily accessible source of project interactions, and developers are often
required to create them by the repository mechanism (e.g., Git).  Additionally, relying only on commit comments makes our approach more generalizable,
as we do not assume the presence of other artifact corpora.
%This is the most readily accessible source of project interactions for outside researchers, since developers often or always (e.g., Git) write such
%message. Our approach is more generalizable if it does not assume the presence of other corpora. 
%bug trackers and email-list archives were not available for both projects. 
An example of a typical commit message, from MySQL, is: \textit{``history annotate diffs bug fixed (if mysql\-\_real\-\_connect() failed there were
two pointers to malloc'ed strings, with memory corruption on free(), of course)''}. 
We extracted these messages and indexed them by creation time. 
We summarized each message as a word distribution minus stop-words such as ``\emph{the}'' and ``\emph{at}''. 
%Stemming was performed in the later stages of our analysis. % WAS IT?

@@

A topic analysis tool such as LDA will try to find $N$ independent
word distributions within the word distributions of all input
messages. 
If there are not $N$ independent word distributions, the topics
produce tend to be duplicates of each other, that is they share the
top terms. During this study we found that when $N$ was 20 we did not
witness duplicate topics very often.
Linear combinations of these $N$ word distributions are meant to represent and recreate the word distributions of any of the original messages. 
These $N$ word distributions effectively form \emph{topics}: cross-cutting collections of words relevant to one or more of our commit messages. 
LDA extracts topics in an unsupervised manner; the algorithm relies
solely on the source data and word distributions of messages, with no human intervention.
